Efficient Calculation of Polynomial Features on Sparse Matrices

### 2016-02-18 paper/workshop/sparse_poly.tex
pruned down to 3 pages

\author{Andrew Nystrom \\
Savvysherpa Inc.\\
6200 Shingle Creek Pkwy \\
Suite 400 \\
Minneapolis, MN 55430, USA \\
\texttt{awnystrom@gmail.com} \\
\And
John Hughes \\
Department of Computer Science \\
Brown University \\
Providence, RI \\
\texttt{jfh@cs.brown.edu} \\
}

@@

We seek a map from matrix indices $(i, j)$ (with $i < j$ and $0 \le i < D$) to numbers $f(i, j)$ with $0 \le f(i, j) < \frac{D(D-1)}{2}$, one that follows the pattern indicated by 
\begin{align}
\begin{bmatrix}
x & 0 & 1 & 3 \\
x & x & 2 & 4 \\
x & x & x & 5 \\
x & x & x & x
\end{bmatrix}
\label{eq:4x4mat}
\end{align}
where the entry in row $i$, column $j$, displays the value $f(i, j)$.

@@

\section{Analysis}
\subsection{Analytical}

@@

\subsection{Empirical}
\section{Conclusion}

>>>>

\author{Andrew Nystrom \\
Savvysherpa Inc.\\
6200 Shingle Creek Pkwy \\
Suite 400 \\
Minneapolis, MN 55430, USA \\
\texttt{awnystrom@gmail.com} \\
\And
John F. Hughes \\
Department of Computer Science \\
Brown University \\
Providence, RI \\
\texttt{jfh@cs.brown.edu} \\
}

@@

For the second degree case, we seek a map from matrix indices $(i, j)$ (with $i < j$ and $0 \le i < D$) to numbers $f(i, j)$ with $0 \le f(i, j) < \frac{D(D-1)}{2}$, one that follows the pattern indicated by 
\begin{align}
\begin{bmatrix}
x & 0 & 1 & 3 \\
x & x & 2 & 4 \\
x & x & x & 5 \\
x & x & x & x
\end{bmatrix}
\label{eq:4x4mat}
\end{align}
where the entry in row $i$, column $j$, displays the value $f(i, j)$.

@@

\section{Complexity Analysis}
%\subsection{Analytical}

@@

%\subsection{Empirical}
%\section{Conclusion}
